A high-repetition-rate, fast temperature-programmed gas chromatograph and its on-line coupling to a supercritical fluid chromatograph (SFC×GC)

### 2020-02-03 Journal/Response2/ResponseLetter2.tex

\begin{quote}
Revision of the paper \meta{RSI19-AR-01677} submitted to the Review of
Scientific Instruments, entitled \PaperTitle{A high-repetition-rate, fast
temperature programmed gas chromatograph and its on-line coupling to a
supercritical fluid chromatograph (SFC×GC)}, based on the referees' report.
\end{quote}

\medskip

\noindent
Dear Chin-Tu Chen:

Thank you for your email dated 30 January 2020 enclosing the reviewers’ comments. We
have carefully reviewed the comments and have revised the manuscript accordingly. Our
responses are given in a point-by-point manner below.

@@

We hope the revised version is now suitable for publication and look forward to hearing from you
in due course.

\vspace{\baselineskip}

\noindent
Yours sincerely,\\
D. Malan\\
Department of Chemistry\\
University of Pretoria

\Reviewer{\#1}
\begin{response}{will [give an] acceptable}
 	The sentence was corrected.
\end{response}

\begin{response}{middle paragraph. The sentence construction is complicated with the nested parentheses.
} 
The parentheses were removed and a sentence providing more detail was added.
\end{response}

\begin{response}{Also the text describes a micro union brazed onto the block,
but the figure shows a drilled and tapped hole.
}  Although the relevant figure was intended to be conceptual in nature, we
agree that a difference between the text and the figure can be confusing. The
figure was changed to match the text.
\end{response}

\begin{response}{p11 digital to analog converter converter . converter is repeated. 
	}  The repeated word was removed. 
\end{response}

\begin{response}{p15. Chromatographically, would it be better if the warmer side of the column was towards the detector or towards the inlet?
	}  
	A sentence and a citation was added to show a possible benefit if the warmer end of the column was towards the inlet.
\end{response}

### 2020-02-03 document.tex
As submitted after second review.

If a chromatographic $^2$D separation is highly orthogonal to the $^1$D
separation, then the $^2$D separation will run into the \textit{general elution
problem}\cite{Skoog2007}: the higher the orthogonality, the more diverse the
compounds found in each $^1$D fraction, and it becomes increasingly unlikely
that one set of acceptable operating conditions (temperature, flow and
stationary phase) will an give acceptable (fast enough and with adequate
resolution) $^2$D separation. In GC×GC as it is practised today this has become
a real problem, known as \textit{wraparound}, a well-known
phenomenon\cite{Dalluege2003}. Wraparound happens when a peak or peaks elute
`late' on the second dimension, so late that the next modulation period has
already started before its elution and the peak only appears on the next $^2$D
chromatogram. Careful interpretation of 2D chromatograms can identify which
peaks can be attributed to wraparound, and adjusting some parameters might
mitigate the problem.

@@

The coaxial heater was made of a \SI{940}{\milli\metre} length of stainless
steel (SAE 304 grade), obtained from MIFAM (Milanówek, Poland). It had an
outside diameter of \SI{1.06}{\milli\metre} and an inside diameter of
\SI{0.80}{\milli\metre}. The ends of the coaxial heater tube terminated in two
identical, specially designed T-piece blocks, machined from brass (See Figure
\ref{fig:Manifold}). These blocks fulfilled three roles:
They (1) sealed the coaxial tube to contain coolant, (2) allowed electrical
connection to the coaxial heater, and (3) acted as a heated transfer line
between the column and the detector and inlet. Each end of the stainless-steel
tube of the coaxial heater was brazed onto a block. The CO$_2$ coolant passed
through one side, and on the opposite side a thermocouple probe inserted into a
blind hole measured the temperature of the block. An electrical contact was
added, to which an electrical conductor could be soft-soldered. Four holes
through the width of the block allowed the fitting of four \SI{220}{\volt},
\SI{100}{\watt} heater cartridges (Hotset), providing each of the two blocks
\SI{400}{\watt} of heating.  The chromatographic capillary column entered the
T-piece block via the bottom port with the coaxial heater tube and passed out
through the top port (where a micro-union using a metal ferrule
(Restek\texttrademark{} SilTite $\mu$-Union Connectors) brazed to the block
created a seal to contain the coolant) and into the inlet or detector.

@@

The electronics for controlling the fast temperature programmed gas
chromatograph and the SFC front-end was developed in-house. A controlled direct
current was used to heat the coaxial heater. The heating circuit consisted of
the coaxial heater in series with a reference resistor and a ballast resistor.
The reference and ballast resistors were constructed from stainless steel wire
with a diameter of \SI{0.5}{\milli\metre}. The reference resistor had multiple,
parallel conductors, the ballast resistor had a bifilar winding, and both had
air cores. These designs (see Figure \ref{fig:RefRes}) minimized electromagnetic
interference and encouraged heat dissipation. Since the coaxial heater
resistance measurement used a two-wire technique, the current-carrying circuit
was made entirely of soldered joints to minimize stray resistance from
developing in electrical connections.

@@

A bank of six PNP 2N2955 bipolar transistors mounted in parallel on an aluminium
plate air-cooled by two 4-inch fans controlled a current of up to
\SI{20}{\ampere} at \SI{20}{\volt} through the coaxial heater. A two-stage
control system controlled the current. The first stage of the control system was
a PID controller implemented in LabVIEW 7.1\texttrademark{} (National
Instruments). The process variable was the temperature of the coaxial heater, as
calculated from its electrical resistance, and the set value was determined by
the desired chromatographic temperature program. The manipulated variable was
the voltage of the digital-to-analog converter converter (DAC) of the data
acquisition board. The final stage was an electronic system, where the voltage
applied to the coaxial heater was the process variable, and the set value was a
voltage provided by the DAC. The manipulated variable was the base current of
the power transistors. In summary, the software set a voltage, which set the
power of the coaxial heater. This two-stage design allows for switching of the
control of the coaxial heater from computer control to manual control by a
potentiometer on the instrument front panel. Being able to control the power of
the coaxial heater manually is extremely useful during development and
fault-finding.

@@

To quantify the non-uniformity of the coaxial heater, a dual thermocouple probe
was inserted into the coaxial heater. The two thermocouples in the probe were
\SI{330}{\milli\metre} apart and positioned in the central third of the coaxial
heater. The coaxial heater was submitted to a repeated program of cooling and
ballistic heating. The recorded data (see Figure \ref{fig:Repeatability}) shows
that the two thermocouples reported different temperatures and that the
difference changed during the heating, implying that the coaxial heater did not
cool or heat perfectly uniformly. But the temperature differences between the
two points were small (approximately \SI{10}{\celsius} at most), stable, and
repeatable and should not prevent good chromatography. These data also show that
ballistic heating is not repeatable enough for gas chromatography, as can be
seen in the variation in temperatures at the end of the heating runs.

@@

% Create the reference section using BibTeX:
%\bibliography{RSI-2019_05}
% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked

@@

%Control: production of article title (-1) disabled
%Control: page (0) single

@@

\begin{thebibliography}{34}%

@@

\providecommand \doibase [0]{http://dx.doi.org/}%

@@

  {Watson}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Horton}}, \
  and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Staples}},\ }in\
  \href {\doibase 10.1109/ULTSYM.1991.234175} {\emph {\bibinfo {booktitle}
  {IEEE 1991 Ultrasonics Symposium,}}},\ Vol.~\bibinfo {volume} {1}\ (\bibinfo
  {year} {1991})\ pp.\ \bibinfo {pages} {305--309}\BibitemShut {NoStop}%

@@

  {He}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Liu}}, \ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ }in\ \href
  {\doibase 10.1109/SPAWDA.2014.6998526} {\emph {\bibinfo {booktitle}
  {Proceedings of the 2014 Symposium on Piezoelectricity, Acoustic Waves, and
  Device Applications}}}\ (\bibinfo {year} {2014})\ pp.\ \bibinfo {pages}
  {59--64}\BibitemShut {NoStop}%

@@

  {\bibfnamefont {S.}~\bibnamefont {Ramos}}, \ and\ \bibinfo {author}
  {\bibfnamefont {B.}~\bibnamefont {Rohrback}},\ }\href {\doibase
  https://doi.org/10.1016/j.fuel.2018.05.102} {\bibfield  {journal} {\bibinfo
  {journal} {Fuel}\ }\textbf {\bibinfo {volume} {231}},\ \bibinfo {pages} {264
  } (\bibinfo {year} {2018})}\BibitemShut {NoStop}%

@@

  {Wang}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\
  }\href {\doibase 10.1093/bja/aeu193} {\bibfield  {journal} {\bibinfo
  {journal} {British Journal of Anaesthesia}\ }\textbf {\bibinfo {volume}
  {113}},\ \bibinfo {pages} {807} (\bibinfo {year} {2014})}\BibitemShut

@@

  {author} {\bibfnamefont {M.}~\bibnamefont {Yan}}, \ and\ \bibinfo {author}
  {\bibfnamefont {X.}~\bibnamefont {Chen}},\ }\href {\doibase
  10.1016/j.chroma.2017.05.001} {\bibfield  {journal} {\bibinfo  {journal}
  {Journal of Chromatography A}\ }\textbf {\bibinfo {volume} {1506}},\ \bibinfo
  {pages} {93} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%

@@

  {Guzek}}, \bibinfo {author} {\bibfnamefont {D.-W.}\ \bibnamefont {Sun}}, \

@@

  }\href {\doibase 10.1111/jfpe.12540} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Food Process Engineering}\ }\textbf {\bibinfo {volume}
  {40}},\ \bibinfo {pages} {e12540} (\bibinfo {year} {2017})},\ \Eprint
  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540}

@@

  {White}},\ }\href

@@

  }\textbf {\bibinfo {volume} {1421}},\ \bibinfo {pages} {129} (\bibinfo {year}
  {2015})}\BibitemShut {NoStop}%

@@

  {Phillips}},\ }\href {\doibase 10.1093/chromsci/29.6.227} {\bibfield

@@

  {\bibinfo {volume} {29}},\ \bibinfo {pages} {227} (\bibinfo {year}

@@

  {Seeley}},\ }\href {\doibase 10.1021/ac303195u} {\bibfield  {journal}
  {\bibinfo  {journal} {Anal. Chem.}\ }\textbf {\bibinfo {volume} {85}},\
  \bibinfo {pages} {557} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%

@@

  {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Pinkerton}}, \ and\ \bibinfo
  {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Synovec}},\ }\href {\doibase
  10.1021/acs.analchem.7b04226} {\bibfield  {journal} {\bibinfo  {journal}
  {Analytical Chemistry}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo {pages}
  {505} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%

@@

  Deursen}}}, \ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
  {Leclercq}},\ }\href {\doibase 10.1016/S0021-9673(99)00227-7} {\bibfield
  {\bibinfo {volume} {856}},\ \bibinfo {pages} {315} (\bibinfo {year}

@@

  {Janssen}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Matisová}},
  \ and\ \bibinfo {author} {\bibfnamefont {U.~A.}\ \bibnamefont {Brinkman}},\
  }\href {\doibase https://doi.org/10.1016/S0165-9936(02)00811-7} {\bibfield

@@

  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {558 } (\bibinfo {year}

@@

  {Giddings}},\ }\href {\doibase 10.1016/0021-9673(95)00249-m} {\bibfield
  {\bibinfo {volume} {703}},\ \bibinfo {pages} {3} (\bibinfo {year}

@@

  {Schoenmakers}},\ }\href {\doibase 10.1016/j.aca.2014.05.048} {\bibfield
  {journal} {\bibinfo  {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo
  {volume} {838}},\ \bibinfo {pages} {93} (\bibinfo {year} {2014})}\BibitemShut

@@

  Deursen}}, \ and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont
  {Brinkman}},\ }\href {\doibase 10.1002/jssc.200301676} {\bibfield  {journal}
  {\bibinfo  {journal} {Journal of Separation Science}\ }\textbf {\bibinfo
  {volume} {27}},\ \bibinfo {pages} {397} (\bibinfo {year} {2004})}\BibitemShut

@@

  {Rohwer}},\ }\href {\doibase 10.1021/ac035538c} {\bibfield  {journal}
  {\bibinfo  {journal} {Analytical chemistry}\ }\textbf {\bibinfo {volume}
  {76}},\ \bibinfo {pages} {3699} (\bibinfo {year} {2004})}\BibitemShut

@@

  {Skoog}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Holler}}, \

@@

  {Dallüge}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beens}}, \

@@

  }\href {\doibase 10.1016/s0021-9673(03)00242-5} {\bibfield  {journal}
  {volume} {1000}},\ \bibinfo {pages} {69} (\bibinfo {year}

@@

  {Venter}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Rohwer}},
  \ and\ \bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont {Laubscher}},\
  }\href {\doibase 10.1016/s0021-9673(99)00137-5} {\bibfield  {journal}

@@

  {volume} {847}},\ \bibinfo {pages} {309} (\bibinfo {year}

@@

  {Klee}},\ }\href {\doibase
  10.1002/1520-667x(2000)12:9<508::aid-mcs5>3.0.co;2-y} {\bibfield  {journal}
  {\bibinfo  {journal} {Journal of Microcolumn Separations}\ }\textbf {\bibinfo
  {volume} {12}},\ \bibinfo {pages} {508} (\bibinfo {year} {2000})}\BibitemShut

@@

  {Wang}}, \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont {Tolley}}, \
  and\ \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont {Lee}},\ }\href
  {\doibase 10.1016/j.chroma.2012.05.021} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo {volume}
  {1261}},\ \bibinfo {pages} {46} (\bibinfo {year} {2012})}\BibitemShut

@@

  {Jacobs}}, \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont {Hilder}},
  \ and\ \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Shellie}},\
  }\href {\doibase 10.1016/j.aca.2013.04.063} {\bibfield  {journal} {\bibinfo

@@

  \bibinfo {pages} {2} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%

@@

  {Górecki}},\ }\href {\doibase 10.1021/acs.analchem.7b02134} {\bibfield
  {volume} {89}},\ \bibinfo {pages} {8207} (\bibinfo {year}

@@

  {Makgwane}}, \ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
  {Rohwer}},\ }\href {\doibase 10.1021/ac051693a} {\bibfield  {journal}
  {78}},\ \bibinfo {pages} {2051} (\bibinfo {year} {2006})}\BibitemShut

@@

  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mustacich}}, \ and\
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Cortes}},\ }\href
  {\doibase 10.1093/chromsci/44.5.253} {\bibfield  {journal} {\bibinfo

@@

  {44}},\ \bibinfo {pages} {253} (\bibinfo {year} {2006})}\BibitemShut

@@

  {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}}, \ and\ \bibinfo

>>>>

If a chromatographic $^2$D separation is highly orthogonal to the $^1$D
separation, then the $^2$D separation will run into the \textit{general elution
problem}\cite{Skoog2007}: the higher the orthogonality, the more diverse the
compounds found in each $^1$D fraction, and it becomes increasingly unlikely
that one set of acceptable operating conditions (temperature, flow and
stationary phase) will an give an acceptable (fast enough and with adequate
resolution) $^2$D separation. In GC×GC as it is practised today this has become
a real problem, known as \textit{wraparound}, a well-known
phenomenon\cite{Dalluege2003}. Wraparound happens when a peak or peaks elute
`late' on the second dimension, so late that the next modulation period has
already started before its elution and the peak only appears on the next $^2$D
chromatogram. Careful interpretation of 2D chromatograms can identify which
peaks can be attributed to wraparound, and adjusting some parameters might
mitigate the problem.

@@

The coaxial heater was made of a \SI{940}{\milli\metre} length of stainless
steel (SAE 304 grade), obtained from MIFAM (Milanówek, Poland). It had an
outside diameter of \SI{1.06}{\milli\metre} and an inside diameter of
\SI{0.80}{\milli\metre}. The ends of the coaxial heater tube terminated in two
identical, specially designed T-piece blocks, machined from brass (See Figure
\ref{fig:Manifold}). These blocks fulfilled three roles:
They (1) sealed the coaxial tube to contain coolant, (2) allowed electrical
connection to the coaxial heater, and (3) acted as a heated transfer line
between the column and the detector and inlet. Each end of the stainless-steel
tube of the coaxial heater was brazed onto a block. The CO$_2$ coolant passed
through one side, and on the opposite side a thermocouple probe inserted into a
blind hole measured the temperature of the block. An electrical contact was
added, to which an electrical conductor could be soft-soldered. Four holes
through the width of the block allowed the fitting of four \SI{220}{\volt},
\SI{100}{\watt} heater cartridges (Hotset), providing each of the two blocks
\SI{400}{\watt} of heating.  The chromatographic capillary column entered the
T-piece block via the bottom port with the coaxial heater tube and passed out
through the top port, where a micro-union using a metal ferrule
(Restek\texttrademark{} SilTite $\mu$-Union Connectors) brazed to the block
created a seal to contain the coolant. From the top port the the column crossed
a small, electrically isolating air gap before entering the inlet or detector.

@@

The electronics for controlling the fast temperature programmed gas
chromatograph and the SFC front-end was developed in-house. A controlled direct
current was used to heat the coaxial heater. The heating circuit consisted of
the coaxial heater in series with a reference resistor and a ballast resistor.
The reference and ballast resistors were constructed from stainless steel wire
with a diameter of \SI{1.0}{\milli\metre}. The reference resistor had multiple,
parallel conductors, the ballast resistor had a bifilar winding, and both had
air cores. These designs (see Figure \ref{fig:RefRes}) minimized electromagnetic
interference and encouraged heat dissipation. Since the coaxial heater
resistance measurement used a two-wire technique, the current-carrying circuit
was made entirely of soldered joints to minimize stray resistance from
developing in electrical connections.

@@

A bank of six PNP 2N2955 bipolar transistors mounted in parallel on an aluminium
plate air-cooled by two 4-inch fans controlled a current of up to
\SI{20}{\ampere} at \SI{20}{\volt} through the coaxial heater. A two-stage
control system controlled the current. The first stage of the control system was
a PID controller implemented in LabVIEW 7.1\texttrademark{} (National
Instruments). The process variable was the temperature of the coaxial heater, as
calculated from its electrical resistance, and the set value was determined by
the desired chromatographic temperature program. The manipulated variable was
the voltage of the digital-to-analog converter (DAC) of the data
acquisition board. The final stage was an electronic system, where the voltage
applied to the coaxial heater was the process variable, and the set value was a
voltage provided by the DAC. The manipulated variable was the base current of
the power transistors. In summary, the software set a voltage, which set the
power of the coaxial heater. This two-stage design allows for switching of the
control of the coaxial heater from computer control to manual control by a
potentiometer on the instrument front panel. Being able to control the power of
the coaxial heater manually is extremely useful during development and
fault-finding.

@@

To quantify the non-uniformity of the coaxial heater, a dual thermocouple probe
was inserted into the coaxial heater. The two thermocouples in the probe were
\SI{330}{\milli\metre} apart and positioned in the central third of the coaxial
heater. The coaxial heater was submitted to a repeated program of cooling and
ballistic heating. The recorded data (see Figure \ref{fig:Repeatability}) shows
that the two thermocouples reported different temperatures and that the
difference changed during the heating, implying that the coaxial heater did not
cool or heat perfectly uniformly. But the temperature differences between the
two points were small (approximately \SI{10}{\celsius} at most), stable, and
repeatable and should not prevent good chromatography. In fact, a small
longitudinal gradient, with the lower temperature nearer the detector, will
produce sharper peaks\cite{Contreras2013}. These data also show that ballistic
heating is not repeatable enough for gas chromatography, as can be seen in the
variation in temperatures at the end of the heating runs.

@@

% Create the reference section using BibTeX:
%\bibliography{RSI-2019_05}
% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BBL file contents start
%aipnum4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst

@@

%Control: production of article title (0) allowed
%Control: page (1) range

@@

\begin{thebibliography}{35}%

@@

\providecommand \doibase [0]{https://doi.org/}%

@@

  {Watson}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Horton}},\
  and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Staples}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Gas chromatography utilizing
  saw sensors},}\ }in\ \href {https://doi.org/10.1109/ULTSYM.1991.234175}
  {\emph {\bibinfo {booktitle} {IEEE 1991 Ultrasonics Symposium,}}},\
  Vol.~\bibinfo {volume} {1}\ (\bibinfo {year} {1991})\ pp.\ \bibinfo {pages}
  {305--309}\BibitemShut {NoStop}%

@@

  {He}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Liu}},\ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {Research progress of saw gas
  charomatography},}\ }in\ \href {https://doi.org/10.1109/SPAWDA.2014.6998526}
  {\emph {\bibinfo {booktitle} {Proceedings of the 2014 Symposium on
  Piezoelectricity, Acoustic Waves, and Device Applications}}}\ (\bibinfo
  {year} {2014})\ pp.\ \bibinfo {pages} {59--64}\BibitemShut {NoStop}%

@@

  {\bibfnamefont {S.}~\bibnamefont {Ramos}},\ and\ \bibinfo {author}
  {\bibfnamefont {B.}~\bibnamefont {Rohrback}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Analysis of biodiesel-diesel blends using ultrafast gas
  chromatography (ufgc) and chemometric methods: Extending astm d7798 to
  biodiesel},}\ }\href
  {https://doi.org/https://doi.org/10.1016/j.fuel.2018.05.102} {\bibfield
  {journal} {\bibinfo  {journal} {Fuel}\ }\textbf {\bibinfo {volume} {231}},\
  \bibinfo {pages} {264 -- 270} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%

@@

  {Wang}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {{Gas chromatograph-surface
  acoustic wave for quick real-time assessment of blood/exhaled gas ratio of
  propofol in humans}},}\ }\href {https://doi.org/10.1093/bja/aeu193}
  {\bibfield  {journal} {\bibinfo  {journal} {British Journal of Anaesthesia}\
  }\textbf {\bibinfo {volume} {113}},\ \bibinfo {pages} {807--814} (\bibinfo
  {year} {2014})}\BibitemShut {NoStop}%

@@

  {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\ and\ \bibinfo {author}
  {\bibfnamefont {X.}~\bibnamefont {Chen}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {{Simultaneous on-line monitoring of propofol and
  sevoflurane in balanced anesthesia by direct resistive heating gas
  chromatography}},}\ }\href {https://doi.org/10.1016/j.chroma.2017.05.001}
  }\textbf {\bibinfo {volume} {1506}},\ \bibinfo {pages} {93--100} (\bibinfo
  {year} {2017})}\BibitemShut {NoStop}%

@@

  {Guzek}}, \bibinfo {author} {\bibfnamefont {D.-W.}\ \bibnamefont {Sun}},\

@@

  }\bibfield  {title} {\enquote {\bibinfo {title} {Differentiation of
  chill-stored and frozen pork necks using electronic nose with ultra-fast gas
  chromatography},}\ }\href {https://doi.org/10.1111/jfpe.12540} {\bibfield
  {journal} {\bibinfo  {journal} {Journal of Food Process Engineering}\
  }\textbf {\bibinfo {volume} {40}},\ \bibinfo {pages} {e12540} (\bibinfo
  {year} {2017})},\ \Eprint
  {https://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540}

@@

  {White}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Evolved gas
  composition monitoring by repetitive injection gas chromatography},}\ }\href

@@

  }\textbf {\bibinfo {volume} {1421}},\ \bibinfo {pages} {129--136} (\bibinfo
  {year} {2015})}\BibitemShut {NoStop}%

@@

  {Phillips}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Comprehensive
  two-dimensional gas chromatography using an on-column thermal modulator
  interface},}\ }\href {https://doi.org/10.1093/chromsci/29.6.227} {\bibfield

@@

  {\bibinfo {volume} {29}},\ \bibinfo {pages} {227--231} (\bibinfo {year}

@@

  {Seeley}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Multidimensional
  gas chromatography: Fundamental advances and new applications},}\ }\href
  {https://doi.org/10.1021/ac303195u} {\bibfield  {journal} {\bibinfo
  {journal} {Anal. Chem.}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo {pages}
  {557--578} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%

@@

  {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Pinkerton}},\ and\ \bibinfo
  {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Synovec}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {Multidimensional gas chromatography:
  Advances in instrumentation, chemometrics, and applications},}\ }\href
  {https://doi.org/10.1021/acs.analchem.7b04226} {\bibfield  {journal}
  {90}},\ \bibinfo {pages} {505--532} (\bibinfo {year} {2018})}\BibitemShut

@@

  Deursen}}},\ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
  {Leclercq}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {High-speed gas
  chromatography: An overview of various concepts},}\ }\href
  {https://doi.org/10.1016/S0021-9673(99)00227-7} {\bibfield  {journal}
  {volume} {856}},\ \bibinfo {pages} {315--329} (\bibinfo {year}

@@

  {Janssen}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Matisová}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Practical fast gas
  chromatography: methods, instrumentation and applications},}\ }\href
  {https://doi.org/https://doi.org/10.1016/S0165-9936(02)00811-7} {\bibfield

@@

  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {558 -- 572} (\bibinfo
  {year} {2002})}\BibitemShut {NoStop}%

@@

  {Giddings}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sample
  dimensionality: A predictor of order-disorder in component peak distribution
  in multidimensional separation},}\ }\href
  {https://doi.org/10.1016/0021-9673(95)00249-m} {\bibfield  {journal}
  {volume} {703}},\ \bibinfo {pages} {3--15} (\bibinfo {year}

@@

  {Schoenmakers}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {A new
  measure of orthogonality for multi-dimensional chromatography},}\ }\href
  {https://doi.org/10.1016/j.aca.2014.05.048} {\bibfield  {journal} {\bibinfo
  {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo {volume} {838}},\
  \bibinfo {pages} {93--101} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%

@@

  Deursen}},\ and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont
  {Brinkman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Automated
  on-line comprehensive two-dimensional {LC}{\texttimes}{GC} and
  {LC}{\texttimes}{GC}-{ToF} {MS}: Instrument design and application to edible
  oil and fat analysis},}\ }\href {https://doi.org/10.1002/jssc.200301676}
  }\textbf {\bibinfo {volume} {27}},\ \bibinfo {pages} {397--409} (\bibinfo
  {year} {2004})}\BibitemShut {NoStop}%

@@

  {Rohwer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Comprehensive
  two-dimensional supercritical fluid and gas chromatography with independent
  fast programmed heating of the gas chromatographic column.}}\ }\href
  {https://doi.org/10.1021/ac035538c} {\bibfield  {journal} {\bibinfo
  {journal} {Analytical chemistry}\ }\textbf {\bibinfo {volume} {76}},\
  \bibinfo {pages} {3699--706} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%

@@

  {Skoog}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Holler}},\

@@

  {Dallüge}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beens}},\

@@

  }\bibfield  {title} {\enquote {\bibinfo {title} {Comprehensive
  two-dimensional gas chromatography: a powerful and versatile analytical
  tool},}\ }\href {https://doi.org/10.1016/s0021-9673(03)00242-5} {\bibfield
  {\bibinfo {volume} {1000}},\ \bibinfo {pages} {69--108} (\bibinfo {year}

@@

  {Venter}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Rohwer}},\
  and\ \bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont {Laubscher}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Analysis of alkane, alkene,
  aromatic and oxygenated groups in petrochemical mixtures by supercritical
  fluid chromatography on silica gel},}\ }\href
  {https://doi.org/10.1016/s0021-9673(99)00137-5} {\bibfield  {journal}

@@

  {volume} {847}},\ \bibinfo {pages} {309--321} (\bibinfo {year}

@@

  {Klee}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Optimal heating
  rate in gas chromatography},}\ }\href
  {https://doi.org/10.1002/1520-667x(2000)12:9<508::aid-mcs5>3.0.co;2-y}
  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Microcolumn
  Separations}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {508--514}
  (\bibinfo {year} {2000})}\BibitemShut {NoStop}%

@@

  {Wang}}, \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont {Tolley}},\
  and\ \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont {Lee}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Gas chromatography using
  resistive heating technology},}\ }\href
  {https://doi.org/10.1016/j.chroma.2012.05.021} {\bibfield  {journal}
  {volume} {1261}},\ \bibinfo {pages} {46--57} (\bibinfo {year}
  {2012})}\BibitemShut {NoStop}%

@@

  {Jacobs}}, \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont {Hilder}},\
  and\ \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Shellie}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Applications of resistive
  heating in gas chromatography: A review},}\ }\href
  {https://doi.org/10.1016/j.aca.2013.04.063} {\bibfield  {journal} {\bibinfo

@@

  \bibinfo {pages} {2--14} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%

@@

  {Górecki}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Temperature
  programming of the second dimension in comprehensive two-dimensional gas
  chromatography},}\ }\href {https://doi.org/10.1021/acs.analchem.7b02134}
  {\bibfield  {journal} {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf
  {\bibinfo {volume} {89}},\ \bibinfo {pages} {8207--8211} (\bibinfo {year}

@@

  {Makgwane}},\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
  {Rohwer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Group-type
  analysis of oxygenated compounds with a silica gel porous layer open tubular
  column and comprehensive two-dimensional supercritical fluid and gas
  chromatography},}\ }\href {https://doi.org/10.1021/ac051693a} {\bibfield
  {volume} {78}},\ \bibinfo {pages} {2051--2054} (\bibinfo {year}
  {2006})}\BibitemShut {NoStop}%

@@

  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mustacich}},\ and\
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Cortes}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {Low thermal mass gas chromatography:
  Principles and applications},}\ }\href
  {https://doi.org/10.1093/chromsci/44.5.253} {\bibfield  {journal} {\bibinfo

@@

  {44}},\ \bibinfo {pages} {253--261} (\bibinfo {year} {2006})}\BibitemShut

@@

  {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}},\ and\ \bibinfo
